---
title: "Data Screening MGCFA"
author: "Erin M. Buchanan"
date: "9/23/2019"
output: html_document
editor_options:
  chunk_output_type: console
---

```{r setup_datascreen, include=FALSE}
# chunk options 
knitr::opts_chunk$set(echo = FALSE, include = FALSE, 
                      cache = TRUE, message = FALSE, warning = FALSE)

## Seed for random number generation
set.seed(37563)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)

# Libraries 
library(mice)
library(dplyr)

# Percent missing function
percentmiss <- function(x){ sum(is.na(x))/length(x) *100 }

# Data Screening Function
## Be sure to put ID column as column 1, source as 2
datascreen <- function(df) {
  
  # Missing Data
  missing <- apply(df, 1, percentmiss)
  ## Rows
  replace_rows <- df[missing <= 5, ]
  dont_replace_rows <- df[missing > 5, ]
  ## Columns
  missing <- apply(replace_rows, 2, percentmiss)
  replace_columns <- replace_rows[ , missing <= 5]
  dont_replace_columns <- cbind(replace_rows[ , 1:2] , replace_rows[ , missing > 5])
  replace_columns <- replace_columns[ , -c(1,2)]
  ## Replacement
  tempnomiss <- mice(replace_columns)
  miced_columns <- complete(tempnomiss, 1)
  all_columns <- cbind(dont_replace_columns, miced_columns)
  ## Put back in the original order
  all_columns <- all_columns[ , colnames(df)] 
  nomiss <- rbind(all_columns, dont_replace_rows)
  ## How many points
  points_estimated <- sum(tempnomiss$where)
  
  # Outliers
  mahal <- mahalanobis(nomiss[ , -c(1:2)],
                       colMeans(nomiss[ , -c(1:2)], na.rm = T),
                       cov(nomiss[ , -c(1:2)], use = "pairwise.complete.obs"))
  cutoff <- qchisq(1-.001, ncol(nomiss[ , -c(1:2)]))
  outliers <- sum(mahal > cutoff, na.rm = T)
  
  # Assumptions
  ## Prep
  random_compare <- rchisq(nrow(nomiss), 7)
  fake <- lm(random_compare ~ ., data = nomiss[ ,-c(1:2)])
  standardized <- rstudent(fake)
  fitted <- scale(fake$fitted.values)

  ## Additivity - in return
  ## Linearity
  qqnorm(standardized); abline(0,1)
  line_plot <- recordPlot()

  ## Normality
  hist(standardized)
  hist_plot <- recordPlot()

  ## Homog + S
  plot(fitted, standardized); abline(0,0); abline(v = 0)
  homogs_plot <- recordPlot()
  
  nomiss$outliers <- mahal
  
  return(list(fulldata = nomiss,
              missing_points = points_estimated,
              num_outliers = outliers,
              correl = summary(fake, correlation = T)$correl, 
              linearity = line_plot,
              normality = hist_plot,
              homogen = homogs_plot))
}

# Import overall file
alldata <- read.csv("./1 manuscript/all_data_combined_edit.csv")
alldata <- subset(alldata,
                  source != "paper")
alldata$source <- droplevels(alldata$source)

# Build a place to put the stuff
summary_ds <- data.frame(scale_name = character(0),
                         sample_size = numeric(),
                         missing_points = numeric(),
                         number_outliers = numeric(),
                         correl = numeric(),
                         linear = character(0),
                         normal = character(0), 
                         homogeneity = character(0),
                         homoscedasticity = character(0),
                         stringsAsFactors = F)
```

```{r ds_bp}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
bp_df <- alldata[ , grepl("partno|source|BP[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
bp_df <- bp_df %>% 
  select(partno, source, everything())

# Reverse Code
## In the qualtrics true = 1, false = 2
## Reverse code the false ones
## False (1): 1, 7, 8, 11, 13, 15, 18, 22, 23, 24 
## True (1): 2, 3, 4, 5, 6, 9, 10, 12, 14, 16, 17, 19, 20, 21, 25, 26, 27, 28
## Plus 2 for the first two columns
bp_df[ , c(1, 7, 8, 11, 13, 15, 18, 22, 23, 24)+2] <- 3 - bp_df[ , c(1, 7, 8, 11, 13, 15, 18, 22, 23, 24)+2] 
## Now change from 2 = false to 0 = false
bp_df[ , -c(1,2)] <- 2 - bp_df[ , -c(1,2)]

# Data Screening
bp_ds <- datascreen(bp_df)

# Make some decisions, save your answers, comment these out
# Note I had to copy this to the console for this to work
# bp_ds$linearity
# bp_ds$normality
# bp_ds$homogen

summary_ds[nrow(summary_ds)+1, ] <- 
                    #scale name, sample size
                    c("BP", sum(!is.na(bp_ds$fulldata$outliers)),
                      # missing points, number outliers
                      bp_ds$missing_points, bp_ds$num_outliers, 
                      # additivity
                      sum(abs(bp_ds$correl) > .90 & abs(bp_ds$correl) < 1), 
                      # linearity, normality, homog, homos
                      "Yes", "Yes", "Yes", "Yes")
```

```{r ds_bpsf}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
bpsf_df <- alldata[ , grepl("partno|source|BPSF[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
bpsf_df <- bpsf_df %>% 
  select(partno, source, everything())

# Reverse Code
## No reverse coded items. 

# Data Screening
bpsf_ds <- datascreen(bpsf_df)

# Make some decisions, save your answers, comment these out
# bpsf_ds$linearity
# bpsf_ds$normality
# bpsf_ds$homogen

summary_ds[nrow(summary_ds)+1, ] <- 
                    #scale name, sample size
                    c("BPSF", sum(!is.na(bpsf_df$fulldata$outliers)),
                      # missing points, number outliers
                      bpsf_ds$missing_points, bpsf_ds$num_outliers, 
                      # additivity
                      sum(abs(bpsf_ds$correl) > .90 & abs(bpsf_ds$correl) < 1), 
                      # linearity, normality, homog, homos
                      "Yes", "No", "Yes", "Yes")
```

```{r ds_brs}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
brs_df <- alldata[ , grepl("partno|source|BRS[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
brs_df <- brs_df %>% 
  select(partno, source, everything())

# Reverse Code
## 1 to 5 scale with items 2, 4, 6 reversed
brs_df[ , c(2,4,6)+2] <- 6 - brs_df[ , c(2,4,6)+2]

# Data Screening
brs_ds <- datascreen(brs_df)

# Make some decisions, save your answers, comment these out
# brs_ds$linearity
# brs_ds$normality
# brs_ds$homogen

summary_ds[nrow(summary_ds)+1, ] <- 
                    #scale name, sample size
                    c("BRS", sum(!is.na(brs_df$fulldata$outliers)),
                      # missing points, number outliers
                      brs_ds$missing_points, brs_ds$num_outliers, 
                      # additivity
                      sum(abs(brs_ds$correl) > .90 & abs(brs_ds$correl) < 1), 
                      # linearity, normality, homog, homos
                      "No", "No", "No", "No")
```

```{r ds_dms}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
dms_df <- alldata[ , grepl("partno|source|DMSTEXT[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
dms_df <- dms_df %>% 
  select(partno, source, everything())

# Reverse Code
## No reverse coding 

# Data Screening
## Deal with text columns
dms_df$DMSTEXT8 <- as.numeric(as.character(dms_df$DMSTEXT8))
dms_df$DMSTEXT11 <- as.numeric(as.character(dms_df$DMSTEXT11))
dms_df$DMSTEXT13 <- as.numeric(as.character(dms_df$DMSTEXT13))
dms_ds <- datascreen(dms_df)

# Make some decisions, save your answers, comment these out
# dms_ds$linearity
# dms_ds$normality
# dms_ds$homogen

summary_ds[nrow(summary_ds)+1, ] <- 
                    #scale name, sample size
                    c("DMS", sum(!is.na(dms_df$fulldata$outliers)),
                      # missing points, number outliers
                      dms_ds$missing_points, dms_ds$num_outliers, 
                      # additivity
                      sum(abs(dms_ds$correl) > .90 & abs(dms_ds$correl) < 1), 
                      # linearity, normality, homog, homos
                      "Yes", "Yes", "No", "Yes")
```

```{r ds_elm}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
elm_df <- alldata[ , grepl("partno|source|ELM[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
elm_df <- elm_df %>% 
  select(partno, source, everything())

# Reverse Code
## No reverse coding 

# Data Screening
## Deal with text columns
elm_ds <- datascreen(elm_df)

# Make some decisions, save your answers, comment these out
# elm_ds$linearity
# elm_ds$normality
# elm_ds$homogen

summary_ds[nrow(summary_ds)+1, ] <- 
                    #scale name, sample size
                    c("ELM", sum(!is.na(elm_df$fulldata$outliers)),
                      # missing points, number outliers
                      elm_ds$missing_points, elm_ds$num_outliers, 
                      # additivity
                      sum(abs(elm_ds$correl) > .90 & abs(elm_ds$correl) < 1), 
                      # linearity, normality, homog, homos
                      "Yes", "Yes", "Yes", "No")
```

```{r ds_elq}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
elq_df <- alldata[ , grepl("partno|source|ELQ[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
elq_df <- elq_df %>% 
  select(partno, source, everything())

# Reverse Code
## Reverse items 2, 7, 14, 18
elq_df[ , c(2, 7, 14, 18)+2] <- 6 - elq_df[ , c(2, 7, 14, 18)+2]

# Data Screening
## Deal with text columns
elq_ds <- datascreen(elq_df)

# Make some decisions, save your answers, comment these out
# elq_ds$linearity
# elq_ds$normality
# elq_ds$homogen

summary_ds[nrow(summary_ds)+1, ] <- 
                    #scale name, sample size
                    c("ELQ", sum(!is.na(elq_df$fulldata$outliers)),
                      # missing points, number outliers
                      elq_ds$missing_points, elq_ds$num_outliers, 
                      # additivity
                      sum(abs(elq_ds$correl) > .90 & abs(elq_ds$correl) < 1), 
                      # linearity, normality, homog, homos
                      "Yes", "Yes", "Yes", "Yes")
```

```{r ds_emas}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
emas_df <- alldata[ , grepl("partno|source|EMAS[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
emas_df <- emas_df %>% 
  select(partno, source, everything())

# Reverse Code
## No reverse coded items

# Data Screening
## Deal with text columns
emas_ds <- datascreen(emas_df)

# Make some decisions, save your answers, comment these out
# emas_ds$linearity
# emas_ds$normality
# emas_ds$homogen

summary_ds[nrow(summary_ds)+1, ] <- 
                    #scale name, sample size
                    c("EMAS", sum(!is.na(emas_df$fulldata$outliers)),
                      # missing points, number outliers
                      emas_ds$missing_points, emas_ds$num_outliers, 
                      # additivity
                      sum(abs(emas_ds$correl) > .90 & abs(emas_ds$correl) < 1), 
                      # linearity, normality, homog, homos
                      "Yes", "Yes", "Yes", "Yes")
```

```{r ds_ems}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
ems_df <- alldata[ , grepl("partno|source|EMS[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
ems_df <- ems_df %>% 
  select(partno, source, everything())

# Reverse Code
## Reverse Code. 1, 4, 7, 8, 9, 10, 13, 17, 19
## The paper says that seven of them were reverse coded but doesn't say which
## These items definitely are reversed given the histograms
ems_df[ , c(1, 4, 7:10, 13, 17, 19)+2] <- 6 - ems_df[ , c(1, 4, 7:10, 13, 17, 19)+2] 

# Data Screening
## Deal with text columns
ems_ds <- datascreen(ems_df)

# Make some decisions, save your answers, comment these out
# ems_ds$linearity
# ems_ds$normality
# ems_ds$homogen

summary_ds[nrow(summary_ds)+1, ] <- 
                    #scale name, sample size
                    c("EMS", sum(!is.na(ems_df$fulldata$outliers)),
                      # missing points, number outliers
                      ems_ds$missing_points, ems_ds$num_outliers, 
                      # additivity
                      sum(abs(ems_ds$correl) > .90 & abs(ems_ds$correl) < 1), 
                      # linearity, normality, homog, homos
                      "Yes", "Yes", "No", "Yes")
```

```{r ds_es}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
es_df <- alldata[ , grepl("partno|source|ES[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
es_df <- es_df %>% 
  select(partno, source, everything())

# Reverse Code
## Reverse Code. 2, 15, 21, 26, 36
es_df[ , c(2, 15, 21, 26, 36)+2] <- 7 - es_df[ , c(2, 15, 21, 26, 36)+2] 

# Data Screening
## Deal with text columns
es_ds <- datascreen(es_df)

# Make some decisions, save your answers, comment these out
# es_ds$linearity
# es_ds$normality
# es_ds$homogen

summary_ds[nrow(summary_ds)+1, ] <- 
                    #scale name, sample size
                    c("ES", sum(!is.na(es_df$fulldata$outliers)),
                      # missing points, number outliers
                      es_ds$missing_points, es_ds$num_outliers, 
                      # additivity
                      sum(abs(es_ds$correl) > .90 & abs(es_ds$correl) < 1), 
                      # linearity, normality, homog, homos
                      "Yes", "No", "No", "No")
```

```{r ds_fom}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
fom_df <- alldata[ , grepl("partno|source|FOM[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
fom_df <- fom_df %>% 
  select(partno, source, everything())

# Reverse Code
## Fix qualtrics coding that's incorrect 1-5 instead of 0-4
fom_df[ , c(1:12)+2] <- fom_df[ , c(1:12)+2] - 1

##Reverse Code. 2, 4, 5, 7, 9 , 11
fom_df[ , c(2, 4, 5, 7, 9, 11)+2] <- 4 - fom_df[ , c(2, 4, 5, 7, 9, 11)+2] 

# Data Screening
## Deal with text columns
fom_ds <- datascreen(fom_df)

# Make some decisions, save your answers, comment thfome out
# fom_ds$linearity
# fom_ds$normality
# fom_ds$homogen

summary_ds[nrow(summary_ds)+1, ] <- 
                    #scale name, sample size
                    c("FOM", sum(!is.na(fom_df$fulldata$outliers)),
                      # missing points, number outliers
                      fom_ds$missing_points, fom_ds$num_outliers, 
                      # additivity
                      sum(abs(fom_ds$correl) > .90 & abs(fom_ds$correl) < 1), 
                      # linearity, normality, homog, homos
                      "Yes", "Yes", "Yes", "Yes")
```

```{r ds_glps}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
glps_df <- alldata[ , grepl("partno|source|GLPS[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
glps_df <- glps_df %>% 
  select(partno, source, everything())

# Reverse Code
## Reverse Code 5, 8, 13
glps_df[ , c(5, 8, 13)+2] <-  8 - glps_df[ , c(5, 8, 13)+2]

# Data Screening
## Deal with text columns
glps_ds <- datascreen(glps_df)

# Make some decisions, save your answers, comment thglpse out
# glps_ds$linearity
# glps_ds$normality
# glps_ds$homogen

summary_ds[nrow(summary_ds)+1, ] <- 
                    #scale name, sample size
                    c("GLPS", sum(!is.na(glps_df$fulldata$outliers)),
                      # missing points, number outliers
                      glps_ds$missing_points, glps_ds$num_outliers, 
                      # additivity
                      sum(abs(glps_ds$correl) > .90 & abs(glps_ds$correl) < 1), 
                      # linearity, normality, homog, homos
                      "Yes", "No", "Yes", "No")
```

```{r ds_lap}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
lap_df <- alldata[ , grepl("partno|source|LAP[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
lap_df <- lap_df %>% 
  select(partno, source, everything())

```

```{r ds_lapr}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
lapr_df <- alldata[ , grepl("partno|source|LAPR[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
lapr_df <- lapr_df %>% 
  select(partno, source, everything())
```

```{r ds_las}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
las_df <- alldata[ , grepl("partno|source|LAS[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
las_df <- las_df %>% 
  select(partno, source, everything())

# Reverse Code
## No reverse coding 

# Data Screening
## Deal with text columns
las_ds <- datascreen(las_df)

# Make some decisions, save your answers, comment thlase out
# las_ds$linearity
# las_ds$normality
# las_ds$homogen

summary_ds[nrow(summary_ds)+1, ] <- 
                    #scale name, sample size
                    c("LAS", sum(!is.na(las_df$fulldata$outliers)),
                      # missing points, number outliers
                      las_ds$missing_points, las_ds$num_outliers, 
                      # additivity
                      sum(abs(las_ds$correl) > .90 & abs(las_ds$correl) < 1), 
                      # linearity, normality, homog, homos
                      "Yes", "Yes", "Yes", "Yes")
```

```{r ds_let}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
let_df <- alldata[ , grepl("partno|source|LET[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
let_df <- let_df %>% 
  select(partno, source, everything())

# Reverse Code
## Reverse code 1, 3, 5
let_df[ , c(1,3,5)+2] <- 6 - let_df[ , c(1,3,5)+2]

# Data Screening
## Deal with text columns
let_ds <- datascreen(let_df)

# Make some decisions, save your answers, comment thlete out
# let_ds$linearity
# let_ds$normality
# let_ds$homogen

summary_ds[nrow(summary_ds)+1, ] <- 
                    #scale name, sample size
                    c("LET", sum(!is.na(let_df$fulldata$outliers)),
                      # missing points, number outliers
                      let_ds$missing_points, let_ds$num_outliers, 
                      # additivity
                      sum(abs(let_ds$correl) > .90 & abs(let_ds$correl) < 1), 
                      # linearity, normality, homog, homos
                      "Yes", "Yes", "No", "No")
```

```{r ds_lpq}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
lpq_df <- alldata[ , grepl("partno|source|LPQ[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
lpq_df <- lpq_df %>% 
  select(partno, source, everything())

# Reverse Code
## Reverse Code. True = 1, False = 2
## 1 Point for True: 3, 4, 6, 7, 10, 13, 17, 18, 20; 
lpq_df[ , c(3,4,6,7,10,13,17,18,20)+2] <- 2 - lpq_df[ , c(3,4,6,7,10,13,17,18,20)+2]
## 1 Point for False: 1, 2, 5, 8, 9, 11, 12, 14, 15, 16, 19
lpq_df[ , c(1,2,5,8,9,11,12,14,15,16,19)+2] <- lpq_df[ , c(1,2,5,8,9,11,12,14,15,16,19)+2] - 1

# Data Screening
## Deal with text columns
lpq_ds <- datascreen(lpq_df)

# Make some decisions, save your answers, comment thlpqe out
# lpq_ds$linearity
# lpq_ds$normality
# lpq_ds$homogen

summary_ds[nrow(summary_ds)+1, ] <- 
                    #scale name, sample size
                    c("lpq", sum(!is.na(lpq_df$fulldata$outliers)),
                      # missing points, number outliers
                      lpq_ds$missing_points, lpq_ds$num_outliers, 
                      # additivity
                      sum(abs(lpq_ds$correl) > .90 & abs(lpq_ds$correl) < 1), 
                      # linearity, normality, homog, homos
                      "Yes", "Yes", "No", "Yes")
```

```{r ds_lri}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
lri_df <- alldata[ , grepl("partno|source|LRI[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
lri_df <- lri_df %>% 
  select(partno, source, everything())

# Reverse Code
## No reverse coding 

# Data Screening
## Deal with text columns
lri_ds <- datascreen(lri_df)

# Make some decisions, save your answers, comment thlrie out
# lri_ds$linearity
# lri_ds$normality
# lri_ds$homogen

summary_ds[nrow(summary_ds)+1, ] <- 
                    #scale name, sample size
                    c("lri", sum(!is.na(lri_df$fulldata$outliers)),
                      # missing points, number outliers
                      lri_ds$missing_points, lri_ds$num_outliers, 
                      # additivity
                      sum(abs(lri_ds$correl) > .90 & abs(lri_ds$correl) < 1), 
                      # linearity, normality, homog, homos
                      "Yes", "No", "No", "No")
```

```{r ds_mapa}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
mapa_df <- alldata[ , grepl("partno|source|MAPA[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
mapa_df <- mapa_df %>% 
  select(partno, source, everything())

# Reverse Code
## First items run 0 through 6
## Second items run 0 through 4
## They are all just one higher than should be
mapa_df[ , c(1:56)+2] <- mapa_df[ , c(1:56)+2] - 1 

# Data Screening
## Deal with text columns
mapa_ds <- datascreen(mapa_df)

# Make some decisions, save your answers, comment thmapae out
# mapa_ds$linearity
# mapa_ds$normality
# mapa_ds$homogen

summary_ds[nrow(summary_ds)+1, ] <- 
                    #scale name, sample size
                    c("MAPA", sum(!is.na(mapa_df$fulldata$outliers)),
                      # missing points, number outliers
                      mapa_ds$missing_points, mapa_ds$num_outliers, 
                      # additivity
                      sum(abs(mapa_ds$correl) > .90 & abs(mapa_ds$correl) < 1), 
                      # linearity, normality, homog, homos
                      "Yes", "No", "No", "No")
```

```{r ds_mili}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
mili_df <- alldata[ , grepl("partno|source|MILI[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
mili_df <- mili_df %>% 
  select(partno, source, everything())

# Reverse Code
## No reverse coded items 

# Data Screening
## Deal with text columns
mili_ds <- datascreen(mili_df)

# Make some decisions, save your answers, comment thmilie out
# mili_ds$linearity
# mili_ds$normality
# mili_ds$homogen

summary_ds[nrow(summary_ds)+1, ] <- 
                    #scale name, sample size
                    c("MILI", sum(!is.na(mili_df$fulldata$outliers)),
                      # missing points, number outliers
                      mili_ds$missing_points, mili_ds$num_outliers, 
                      # additivity
                      sum(abs(mili_ds$correl) > .90 & abs(mili_ds$correl) < 1), 
                      # linearity, normality, homog, homos
                      "Yes", "No", "No", "No")
```

```{r ds_milq}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
milq_df <- alldata[ , grepl("partno|source|MILQ[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
milq_df <- milq_df %>% 
  select(partno, source, everything())

# Reverse Code
## Just number 9
milq_df[ , 9+2] <- 8 - milq_df[ , 9+2]

# Data Screening
## Deal with text columns
milq_ds <- datascreen(milq_df)

# Make some decisions, save your answers, comment thmilqe out
# milq_ds$linearity
# milq_ds$normality
# milq_ds$homogen

summary_ds[nrow(summary_ds)+1, ] <- 
                    #scale name, sample size
                    c("MILQ", sum(!is.na(milq_df$fulldata$outliers)),
                      # missing points, number outliers
                      milq_ds$missing_points, milq_ds$num_outliers, 
                      # additivity
                      sum(abs(milq_ds$correl) > .90 & abs(milq_ds$correl) < 1), 
                      # linearity, normality, homog, homos
                      "Yes", "Yes", "No", "No")
```

```{r ds_mils}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
mils_df <- alldata[ , grepl("partno|source|MILS[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
mils_df <- mils_df %>% 
  select(partno, source, everything())

# Reverse Code
## Just number 9
mils_df[ , 15+2] <- 6 - mils_df[ , 15+2]

# Data Screening
## Deal with text columns
mils_ds <- datascreen(mils_df)

# Make some decisions, save your answers, comment thmilse out
# mils_ds$linearity
# mils_ds$normality
# mils_ds$homogen

summary_ds[nrow(summary_ds)+1, ] <- 
                    #scale name, sample size
                    c("MILS", sum(!is.na(mils_df$fulldata$outliers)),
                      # missing points, number outliers
                      mils_ds$missing_points, mils_ds$num_outliers, 
                      # additivity
                      sum(abs(mils_ds$correl) > .90 & abs(mils_ds$correl) < 1), 
                      # linearity, normality, homog, homos
                      "Yes", "Yes", "No", "No")
```

```{r ds_ml}
# Data
## Expression is partno | (or) put in the letters you want, leave numbers
ml_df <- alldata[ , grepl("partno|source|ML[0-9]+", colnames(alldata))]
## Make sure partno and source are at the beginning
ml_df <- ml_df %>% 
  select(partno, source, everything())

# Reverse Code
## Just number 9
ml_df[ , 15+2] <- 6 - ml_df[ , 15+2]

# Data Screening
## Deal with text columns
ml_ds <- datascreen(ml_df)

# Make some decisions, save your answers, comment thmle out
# ml_ds$linearity
# ml_ds$normality
# ml_ds$homogen

summary_ds[nrow(summary_ds)+1, ] <- 
                    #scale name, sample size
                    c("ML", sum(!is.na(ml_df$fulldata$outliers)),
                      # missing points, number outliers
                      ml_ds$missing_points, ml_ds$num_outliers, 
                      # additivity
                      sum(abs(ml_ds$correl) > .90 & abs(ml_ds$correl) < 1), 
                      # linearity, normality, homog, homos
                      "Yes", "Yes", "No", "No")
```


ML	Warner, S. C., & Williams, J. I. (1987). The meaning in life scale: determining the reliability and validity of a measure. Journal of Chronic Diseases, 40(6), 503-512.
MLK	Krause, N. (2004). Stressors arising in highly valued roles, meaning in life, and the physical health status of older adults. The Journals of Gerontology Series B: Psychological Sciences and Social Sciences, 59(5), S287-S297.
MLM	Morgan, J., & Farsides, T. (2007). Measuring meaning in life. Journal of Happiness Studies, 10(2), 197-214.
MLQ	Steger, M. F., Frazier, P., Oishi, S., & Kaler, M. (2006). The meaning in life questionnaire: Assessing the presence of and search for meaning in life. Journal of Counseling Psychology, 53(1), 80-93.
MLT	Tomich, P. L., & Helgeson, V. S. (2002). Five years later: a cross‐sectional comparison of breast cancer survivors with healthy women. Psycho‐oncology, 11(2), 154-169.
MMM	Brown, G. P., Roach, A., Irving, L., & Joseph, K. (2008). Personal meaning: a neglected transdiagnostic construct. International Journal of Cognitive Therapy, 1(3), 223-236.
MMS	van den Heuvel, M., Demerouti, E., Schreurs, B. H., Bakker, A. B., & Schaufeli, W. B. (2009). Does meaning-making help during organizational change?: Development and validation of a new scale. Career Development International, 14(6), 508-533.
NoM &NeM	Kunzendorf, R. G., Moran, C., & Gray, R. (1995). Personality traits and reality-testing abilities, controlling for vividness of imagery. Imagination, Cognition and Personality, 15(2), 113-131.
OHS	Peterson, C., Park, N., & Seligman, M. E. (2005). Orientations to happiness and life satisfaction: The full life versus the empty life. Journal of happiness studies, 6(1), 25-41.
PIL	Crumbaugh, J. C., & Maholick, L. T. (1964). An experimental study in existentialism: The psychometric approach to Frankl's concept of noogenic neurosis. Journal of clinical psychology, 20(2), 200-207.
PILSF	Schulenberg, S. E., Schnetzer, L. W., & Buchanan, E. M. (2011). The purpose in life test-short form: Development and psychometric support. Journal of Happiness Studies, 12(5), 861-876.
PPMS	Wong, P. P. (1998). Implicit theories of meaningful life and the development of the personal meaning profile. In P. P. Wong, P. S. Fry (Eds.) , The human quest for meaning: A handbook of psychological research and clinical applications (pp. 111-140). Mahwah, NJ US: Lawrence Erlbaum Associates Publishers.
PVS III-R	Maddi, S. R., Harvey, R. H., Khoshaba, D. M., Lu, J. L., Persico, M., & Brow, M. (2006). The Personality Construct of Hardiness, III: Relationships With Repression, Innovativeness, Authoritarianism, and Performance. Journal Of Personality, 74, 575-598. doi:10.1111/j.1467-6494.2006.00385.x
PWS	Ryff, C. D. (1989). Happiness is everything, or is it? Explorations on the meaning of psychological well-being. Journal of personality and social psychology, 57(6), 1069.
QEWB	Waterman, A. S., Schwartz, S. J., Zamboanga, B. L., Ravert, R. D., Williams, M. K., Bede Agocha, V., ... & Brent Donnellan, M. (2010). The Questionnaire for Eudaimonic Well-Being: Psychometric properties, demographic comparisons, and evidence of validity. The Journal of Positive Psychology, 5(1), 41-61.
RS14	Wagnild, G. M. (2011). The Resilience Scale User's Guide: For the US English Version of the Resilience Scale and the 14-item Resilience Scale (RS-14). P. E. Guinn (Ed.). Resilience Center.
SCS	Antonovsky, A. (1993). The structure and properties of the sense of coherence scale. Social science & medicine, 36(6), 725-733.
SMS	Mascaro, N., Rosen, D. H., & Morey, L. C. (2004). The development, construct validity, and clinical utility of the spiritual meaning scale. Personality and Individual Differences, 37(4), 845-860.
SOMP	"Reker, G. T. (1988, November). Sources of personal meaning among middle-aged and older adults: A replication. In Annual Meeting of the Gerontological Society of America, San Francisco, CA.  
Reker, G. T., & Wong, P. T. P. (1988). Aging as an individual process: Toward a theory of personal meaning. In J. E. Birren & V. L. Bengtson (Eds.), Emergent theories of aging (pp. 214-246). New York, NY: Springer."
SONG	Crumbaugh, J. C. (1977). The seeking of noetic goals test (SONG): A complementary scale to the purpose in life test (PIL). Journal of Clinical Psychology, 33(3), 900-907.
STMS	Li, H. (2002). College stress and psychological well-being: Vision in life as a coping resource (Doctoral dissertation, University of Hong Kong).
STMS 2	Li, H. (2002). College stress and psychological well-being: Vision in life as a coping resource (Doctoral dissertation, University of Hong Kong).
SWLS	Diener, E. D., Emmons, R. A., Larsen, R. J., & Griffin, S. (1985). The satisfaction with life scale. Journal of personality assessment, 49(1), 71-75.
VOL	Lawton, M. P., Moss, M., Hoffman, C., Kleban, M. H., Ruckdeschel, K., & Winter, L. (2001). Valuation of Life. Journal of Aging and Health, 13(1), 3-31.